Privacy-Preserving Localisation Using Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-10-15 main.tex
Added remark about implicit weight w=1 - also referenced the remark in the algorithm

@@

    \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$, encrypting them for aggregation, and sending them back to the navigator. Care must be taken when encoding during homomorphic operations to ensure fractional factor $m$ satisfies \eqref{eqn:encoding_homomorphic_add}. This is described by Algorithm \ref{alg:measurement_info}.

@@

    \State Let $\beta_{v1}^{(i)}$ represent an encryption of element $(v,1)$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}^3)}
    (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(-2\rv{r}_{k, i}^{-1}s_{x,i}\rv{z}_{k,i}')}
    H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
    \State Compute $\beta_{21}^{(i)}$ using \eqref{eqn:hrz_linear_comb} and \eqref{eqn:our_scheme_lin_comb} in the form above
    \For{$v \gets 1$ to $2$}
        \State Send $\beta_{v1}$ to the navigator
    \EndFor

    \State Let $\alpha_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
    \State $\alpha_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
    \State Compute remaining $\alpha_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb} and \eqref{eqn:our_scheme_lin_comb} in the form above
    \For{$v \gets 1$ to $2$}
        \For{$w \gets 1$ to $2$} 
            \State Send $\alpha_{vw}^{(i)}$ to the navigator
        \EndFor
    \EndFor
    \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Leakage} \label{subsec:leakage}
With the algorithm defined, we can analyse the localisation leakage when the strictly defined LCAO leakage is taken into account. We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}. Consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage. Honest-but-curious sensors are not required for scheme security, but avoid the possibility of malicious sensors gaining prior knowledge about remaining sensor measurements. This is possibly achieved by detecting changes in real measurements after reporting false measurements to the navigator. As stated in Section \ref{subsec:capabilities}, misbehaving sensors are a known problem which complicates homomorphic operations and active malicious sensors are not considered in the scope of this work.

>>>>

\begin{rem} \label{rem:lcao_implicit_weight}
    The construction of this scheme additionally supports the linear combination of the implicit weight, $\omega^{(t)}_j = 1$, by replacing
    \begin{equation}
        \mathcal{E}_{pk_0}(1)^{x^{(t)}_{i,j}} = (N+1)^{1}r_j^N \pmod{N^2}
    \end{equation}
    in \eqref{eqn:our_scheme_lin_comb} by
    \begin{equation}
        (N+1)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
    \end{equation}
    due to the removal of $r_j^N$ terms during decryption. This can be used to reduce the broadcast communication cost by one weight.
\end{rem}

@@

    \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$, encrypting them for aggregation, and sending them back to the navigator. Care must be taken when encoding during homomorphic operations to ensure fractional factor $m$ satisfies \eqref{eqn:encoding_homomorphic_add}, in particular when using the property from Remark \ref{rem:lcao_implicit_weight}. This is described by Algorithm \ref{alg:measurement_info}.

@@

    \State Let $\beta_{v1}^{(i)}$ represent an encryption of element $(v,1)$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}^3)}
    (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(-2\rv{r}_{k, i}^{-1}s_{x,i}\rv{z}_{k,i}')}
    H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
    \State Compute $\beta_{21}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
    \For{$v \gets 1$ to $2$}
        \State Send $\beta_{v1}$ to the navigator
    \EndFor

    \State Let $\alpha_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
    \State $\alpha_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_{x,i}^2)}\cdot$\par
    \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
    \State Compute remaining $\alpha_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
    \For{$v \gets 1$ to $2$}
        \For{$w \gets 1$ to $2$} 
            \State Send $\alpha_{vw}^{(i)}$ to the navigator
        \EndFor
    \EndFor
    \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\subsection{Leakage} \label{subsec:leakage}
With the algorithm defined, we can analyse the localisation leakage when the strictly defined LCAO leakage is taken into account. We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}. Consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage. Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining prior knowledge about remaining sensor measurements. This is possibly achieved by detecting changes in real measurements after reporting false measurements to the navigator. As stated in Section \ref{subsec:capabilities}, misbehaving sensors are a known problem which complicates homomorphic operations and active malicious sensors are not considered in the scope of this work.
